A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-04 paper.tex
fix gls entries

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (\nht) from the agriculture sector. Again, the
\gls{sas} region shows a large discrepancy in the harmonization year ($>$150\%
in this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the \gls{sas} trajectory,
it largely affects the post-2080 shape of the global trajectory (Figure
\ref{fig:nh3}, Panel \textbf{b}). For example, in the original model result,
\gls{SAS} \nht agricultural emissions contribute $\sim$30\% of total global
emissions, whereas in the unharmonized case with default methods, \gls{SAS}
comprises $\sim$50\% of global emissions. By using a \code{constant_offset}
method as an override, this distortion is addressed and more accurately reflects
unharmonized results in the \gls{sas} region, the relative importance between
regions, and global results for agricultural ammonia emissions, each of which
contributes to a better harmonization quality for the harmonized \gls{sas}
trajectory. The harmonized emissions using overrides result in a contribution of
$\sim$32\% of total global emissions by the \gls{SAS} region which aligns
closely with the unharmonized model results.

>>>>

In certain circumstances, the application of the default harmonization methods
can affect not only the magnitude but also the shape of regional
trajectories. Figure \ref{fig:nh3} shows an example case of emissions
trajectories for ammonia (\nht) from the agriculture sector. Again, the
\gls{sas} region shows a large discrepancy in the harmonization year ($>$150\%
in this case). The resulting trajectory harmonized with the default method
(\code{constant_ratio}) provides a large increase after 2080 in the SSP2
reference scenario. Notably, the SSP2-45 scenario is not affected to the same
degree. While this distortion changes the magnitude of the \gls{sas} trajectory,
it largely affects the post-2080 shape of the global trajectory (Figure
\ref{fig:nh3}, Panel \textbf{b}). For example, in the original model result,
\gls{sas} \nht agricultural emissions contribute $\sim$30\% of total global
emissions, whereas in the unharmonized case with default methods, \gls{sas}
comprises $\sim$50\% of global emissions. By using a \code{constant_offset}
method as an override, this distortion is addressed and more accurately reflects
unharmonized results in the \gls{sas} region, the relative importance between
regions, and global results for agricultural ammonia emissions, each of which
contributes to a better harmonization quality for the harmonized \gls{sas}
trajectory. The harmonized emissions using overrides result in a contribution of
$\sim$32\% of total global emissions by the \gls{sas} region which aligns
closely with the unharmonized model results.
